Kindly Bent to Free Us

### 2019-11-23 kindly/lang.tex
Pairs are back!

A borrow $\borrow{x}$ is always taken from a variable $x$. The
\emph{borrow annotation} $\BORROW$ indicates whether the borrow is exclusive
($\MBORROW$) or shared ($\IBORROW$). If $x$ is already borrowed,
then we need to use the reborrow expression $\reborrow{x}$.
%
A region $\region{\Sone x\BORROW}{e}$ is annotated with its nesting $n$, the variable $x$ that may be borrowed in $e$, and the kind of borrow $\BORROW$.
%
% A match is indexed with a \emph{match specification} $\etransfm$ that indicates
% whether the match should work on borrows ($\etransfm=\&^b$) or not ($\etransfm=id$).
%
We consider four primitive operations to manipulate resources:
$\create$, $\observe$, $\update$ and $\destroy$.

@@

Splitting applies whenever an
expression has multiple subexpressions:  function applications,
and let bindings. In the
expression
$\letin{a}{\text{create}\ 8\ x}
{f\ \region[{}]{\Sone a\IBORROW}{\text{length}\ \borrow[\IBORROW]{a}}\ a}$,
the rule {\sc Susp} splits off a borrow from  the resource
$a$ to use it in the left argument.
As usual, a borrow cannot be active in the same scope as its resource.
The \emph{region} around its use ensures that the borrow in the left argument
does not
escape, which brings us to the next topic.

@@

Let-polymorphism is demonstrated for functions giving rise to elaborated
$\eletfun$ expressions annotated with a type scheme $\schm$ and a kind $k$ indicating their
usage restriction (linear, affine, etc) relative to the variables and
constraints of $\schm$. Their use
gives rise to explicit instantiation of the kind and type variables.
% Pairs come with a kind tag $k$ indicating the usage restriction.

>>>>

A borrow $\borrow{x}$ is always taken from a variable $x$. The
\emph{borrow annotation} $\BORROW$ indicates whether the borrow is exclusive
($\MBORROW$) or shared ($\IBORROW$). If $x$ is already borrowed,
then we need to use the reborrow expression $\reborrow{x}$.
%
A region $\region{\Sone x\BORROW}{e}$ is annotated with its nesting $n$, the variable $x$ that may be borrowed in $e$, and the kind of borrow $\BORROW$.
%
A match is indexed with a \emph{match specification} $\etransfm$ that indicates
whether the match should work on borrows ($\etransfm=\&^b$) or not ($\etransfm=id$).
%
We consider four primitive operations to manipulate resources:
$\create$, $\observe$, $\update$ and $\destroy$.

@@

Splitting applies whenever an
expression has multiple subexpressions:  function applications,
let bindings and pairs. In the
expression
$\letin{a}{\text{create}\ 8\ x}
{f\ \region[{}]{\Sone a\IBORROW}{\text{length}\ \borrow[\IBORROW]{a}}\ a}$,
the rule {\sc Susp} splits off a borrow from  the resource
$a$ to use it in the left argument.
As usual, a borrow cannot be active in the same scope as its resource.
The \emph{region} around its use ensures that the borrow in the left argument
does not
escape, which brings us to the next topic.

@@

Let-polymorphism is demonstrated for functions giving rise to elaborated
$\eletfun$ expressions annotated with a type scheme $\schm$ and a kind $k$ indicating their
usage restriction (linear, affine, etc) relative to the variables and
constraints of $\schm$. Their use
gives rise to explicit instantiation of the kind and type variables.
Pairs come with a kind tag $k$ indicating the usage restriction.
